### 2018-06-01 submission/manuscript.Rmd
update figure legends

**Figure 1: Total Number of OTUs in Fecal Samples by Number of Cycles.** The points represent the median number of OTUs of all four fecal samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This increased range also was larger for specific HiFi DNA polymerases.

**Figure 2:  Total Number of OTUs in Mock Samples by Number of Cycles.** The points represent the median number of OTUs for the mock samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The dotted black line represents the number of OTUs detected when only the references sequences for the mock community are clustered. The range in the number of OTUs detected in the mock samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

**Figure 3: Bray-Curtis Community Differences by Five-Cycle Intervals.** A) within person differences based on the next 5-cycle PCR interval in fecal samples. B) Within replicate difference based on the next 5-cycle PCR interval in mock samples. The points represent the median Bray-Curtis index for the samples. The lines represent the range of the minimum and maximum Bray-Curtis index value for each PCR 5-cycle increment comparison. The closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar the bacterial community is of the two compared number of cycles.

**Figure 4: HiFi DNA Polymerase Error Rate in Mock Samples.** The error bars represent the 75% interquartile range of the median error rate.

**Figure 5: HiFi DNA Polymerase Chimera Prevalence in Mock Samples.** A) Percentage of chimeric sequences without the removal of chimeras with VSEARCH. C) Percentage of chimeric sequences with the removal of chimeras with VSEARCH. C) The total percent of chimeric sequences removed with VSEARCH by cycle number. The error bars represent the 75% interquartile range of the median.

**Figure 6: The Correlation between Number of OTUs and Chimeras in Mock Samples.**

@@

**Figure S1: HiFi DNA Polymerase Nucleotide Subsitutions in Mock Samples.**

>>>>

**Figure 1: The number and range of OTUs in fecal samples varies by polymerase.** The points represent the median number of OTUs of all four fecal samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This increased range also was larger for specific HiFi DNA polymerases.

**Figure 2: The number and range of OTUs in mock samples varies by polymerase.** The points represent the median number of OTUs for the mock samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The dotted black line represents the number of OTUs detected when only the references sequences for the mock community are clustered. The range in the number of OTUs detected in the mock samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

**Figure 3: Lower five-cycle intervals have larger differences than higher five-cycle intervals using Bray-Curtis.** A) within person differences based on the next 5-cycle PCR interval in fecal samples. B) Within replicate difference based on the next 5-cycle PCR interval in mock samples. The points represent the median Bray-Curtis index for the samples. The lines represent the range of the minimum and maximum Bray-Curtis index value for each PCR 5-cycle increment comparison. The closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar the bacterial community is of the two compared number of cycles.

**Figure 4: Variation in error rate by polymerase in mock community samples are similar across the number of cycles used.** The error bars represent the 75% interquartile range of the median error rate.

**Figure 5: Chimera prevalence varies by polymerase and increases with higher number of cycles used.** A) Percentage of chimeric sequences without the removal of chimeras with VSEARCH. C) Percentage of chimeric sequences with the removal of chimeras with VSEARCH. C) The total percent of chimeric sequences removed with VSEARCH by cycle number. The error bars represent the 75% interquartile range of the median.

**Figure 6: Regardless of polymerase used the higher the chimera prevalence the higher the observed number of OTUs in mock community samples.**

@@

**Figure S1: No preference for specific base subsitutions was observed across the polymerases in mock community samples.**

### 2018-06-01 submission/manuscript.tex
update figure legends

\textbf{Figure 1: Total Number of OTUs in Fecal Samples by Number of
Cycles.} The points represent the median number of OTUs of all four
fecal samples. The lines represent the range of the minimum and maximum
number of OTUs detected within the four fecal samples. The range in the
number of OTUs detected in the different fecal samples increased as
cycle number increased. This increased range also was larger for
specific HiFi DNA polymerases.

\textbf{Figure 2: Total Number of OTUs in Mock Samples by Number of
Cycles.} The points represent the median number of OTUs for the mock
samples. The lines represent the range of the minimum and maximum number
of OTUs detected within the four fecal samples. The dotted black line
represents the number of OTUs detected when only the references
sequences for the mock community are clustered. The range in the number
of OTUs detected in the mock samples increased as cycle number
increased. This range was also larger for specific HiFi DNA polymerases.

\textbf{Figure 3: Bray-Curtis Community Differences by Five-Cycle
Intervals.} A) within person differences based on the next 5-cycle PCR
interval in fecal samples. B) Within replicate difference based on the
next 5-cycle PCR interval in mock samples. The points represent the
median Bray-Curtis index for the samples. The lines represent the range
of the minimum and maximum Bray-Curtis index value for each PCR 5-cycle
increment comparison. The closer a sample is to a Bray-Curtis index of
1.00 the more dissimilar the bacterial community is of the two compared
number of cycles.

\textbf{Figure 4: HiFi DNA Polymerase Error Rate in Mock Samples.} The
error bars represent the 75\% interquartile range of the median error
rate.

\textbf{Figure 5: HiFi DNA Polymerase Chimera Prevalence in Mock
Samples.} A) Percentage of chimeric sequences without the removal of
chimeras with VSEARCH. C) Percentage of chimeric sequences with the
removal of chimeras with VSEARCH. C) The total percent of chimeric
sequences removed with VSEARCH by cycle number. The error bars represent
the 75\% interquartile range of the median.

\textbf{Figure 6: The Correlation between Number of OTUs and Chimeras in
Mock Samples.}

@@

\textbf{Figure S1: HiFi DNA Polymerase Nucleotide Subsitutions in Mock
Samples.}

>>>>

\textbf{Figure 1: The number and range of OTUs in fecal samples varies
by polymerase.} The points represent the median number of OTUs of all
four fecal samples. The lines represent the range of the minimum and
maximum number of OTUs detected within the four fecal samples. The range
in the number of OTUs detected in the different fecal samples increased
as cycle number increased. This increased range also was larger for
specific HiFi DNA polymerases.

\textbf{Figure 2: The number and range of OTUs in mock samples varies by
polymerase.} The points represent the median number of OTUs for the mock
samples. The lines represent the range of the minimum and maximum number
of OTUs detected within the four fecal samples. The dotted black line
represents the number of OTUs detected when only the references
sequences for the mock community are clustered. The range in the number
of OTUs detected in the mock samples increased as cycle number
increased. This range was also larger for specific HiFi DNA polymerases.

\textbf{Figure 3: Lower five-cycle intervals have larger differences
than higher five-cycle intervals using Bray-Curtis.} A) within person
differences based on the next 5-cycle PCR interval in fecal samples. B)
Within replicate difference based on the next 5-cycle PCR interval in
mock samples. The points represent the median Bray-Curtis index for the
samples. The lines represent the range of the minimum and maximum
Bray-Curtis index value for each PCR 5-cycle increment comparison. The
closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar
the bacterial community is of the two compared number of cycles.

\textbf{Figure 4: Variation in error rate by polymerase in mock
community samples are similar across the number of cycles used.} The
error bars represent the 75\% interquartile range of the median error
rate.

\textbf{Figure 5: Chimera prevalence varies by polymerase and increases
with higher number of cycles used.} A) Percentage of chimeric sequences
without the removal of chimeras with VSEARCH. C) Percentage of chimeric
sequences with the removal of chimeras with VSEARCH. C) The total
percent of chimeric sequences removed with VSEARCH by cycle number. The
error bars represent the 75\% interquartile range of the median.

\textbf{Figure 6: Regardless of polymerase used the higher the chimera
prevalence the higher the observed number of OTUs in mock community
samples.}

@@

\textbf{Figure S1: No preference for specific base subsitutions was
observed across the polymerases in mock community samples.}
